---
title: "Data Products - Week 4 Project"
author: "Ryan Savio"
date: "March 1, 2020"
output:
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(readr)
library(tseries)
library(forecast)
```

## Overview
My shiny application forecasts closing prices for 'FAANG' technology stocks.

The user can use the provided drop-down menu to select which stock they wish to review. As well as adjusted the number of periods to be forecast.

The application can be found at https://rsavio.shinyapps.io/DP4_proj/

With the source files published on to [GitHub](https://github.com/rasavio/DP4_Proj) for reference.

## Data Source

The data snapshot used by the web application contains stock prices from 01/01/2010 to 01/03/2020. 

```{r, eval=FALSE}
# FAANG Technology stocks
stock_symbols <- c("FB", "AMZN", "NFLX", "GOOG", "AAPL")

data <- tq_get(
  stock_symbols,
  get  = "stock.prices",
  from = "2010-01-01")
```

## Forecasting
Forecasting is generated in realtime using `ARIMA` based on user selections.
```{r, eval=FALSE}
serverLogic <- function(input, output) {
  output$g <- renderPlot({
    # filter data for selected stock
    input_data <- data %>%
      filter(symbol == input$stock)
    # generate forecast
    fit <- auto.arima(input_data$close)
        forecast <- forecast(fit, h = input$periods)
    # draw plot
    g <- plot(forecast, ylab = "Closing Price", xlab = "Period")
    g
  })
}
```
## User Instructions

There are only two input variables, each with default values selected so that an example is generated upon loading the web application.

Within the `server.R` file we have configured the application to filter the data snapshot based on the selected stock symbol. The ARIMA model is then re-fit based on the selection, as well as the defined number of periods.

Once the model is fit a simple plot is generated to display both the actual and forecast closing stock prices.

## Sample
Here's an example based on the selection of Facebook ("FB") for 250 periods.

```{r}
data <- read_rds("data.rds") %>%
  filter(symbol == "FB")

fit <- auto.arima(data$close)
forecast <- forecast(fit, h = 250)
plot(forecast, ylab = "Closing Price", xlab = "Period")
```



